---
title: "Simulations of Wilson vs. Wald CI Intervals"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulations of Wilson vs. Wald CI Intervals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In "Wilson Confidence Intervals for Binomial
Proportions With Multiple Imputation for Missing
Data" (A. Lott & J. Reiter, 2018), the authors run simulation studies comparing coverage of MI-Wilson and MI-Wald confidence intervals, among a few other slight variations of the two. This is good motivation for using the `phat` versions of the `mi_wilson` and `mi_wald` functions. While we don't implement the simulations here, we lay out a foundation and demonstrate one use of the `mi_wald_phat` and `mi_wilson_phat` functions.

We first load the MI-Wilson library as follows:

```{r setup}
library(MIWilson)
```

We then create a simple master dataset with binary values and induce MCAR missingness; this is carried out by the `create_missing_data` function. With the incomplete master dataset, we create multiple imputations using Bayesian principles (see paper for details), using the `create_imps` function. 

```{r}
#creating missing data
create_missing_data <- function(n, p, m, MIA_perc) {
  
  complete = incomplete = rbinom(n, 1, p)
  
  #setting up number of missing values, dataset with missing values
  blanks = floor(MIA_perc * n)
  idcs = 1:length(complete)
  incomplete[sample(idcs, blanks)] = NA
  
  return(incomplete)

}


#creating multiple imputations
create_imps <- function(n, m, incomplete) {
  
  count_one = table(incomplete)[2]
  count_zero = table(incomplete)[1]
  
  imputations = matrix(nrow = n, ncol = m)
  for (i in 1:m) {
    p_star = rbeta(1, count_one + 1, count_zero + 1)
    incomp_idx = which(is.na(incomplete))
    
    curr_imp = incomplete
    curr_imp[incomp_idx] = rbinom(length(incomp_idx), 1, p_star)
    
    imputations[,i] = curr_imp
  }
  
  return(imputations)
  
}

```

```{r}
n = 100
p = 0.5
m = 10
MIA_perc = 0.3

incomplete = create_missing_data(n, p, m, MIA_perc)
imputations = create_imps(n, m, incomplete)

phats = colSums(imputations)/nrow(imputations)
mi_wald_phat(phats = phats, n = nrow(imputations))
mi_wilson_phat(phats = phats, n =nrow(imputations))
```

